{Good covers and algebras on conically smooth spaces}

### 2025-09-10 paperversion/paper.tex
typo

\begin{lemma}\label{FBLD2TE}
    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for all geodesic disks $D\subset\R^n$ about the origin the intersections
    \begin{enumerate}
        \item $D\cap (\R^{n-c}\times(\R^{c}\smallsetminus\R^{c}_{\geq0}))$
        \item $D \cap (\R^{n-c}\times\R^{c}_{>0})$
    \end{enumerate}
    are disks.
\end{lemma}
\begin{proof}
    Let us suppose $n=c$ for simplicity. For $r>0$, recall the diffeomorphism $[0,r)\to[0,\infty)$, $x\mapsto\frac{x}{r-x}$. In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x:\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric. Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
\end{proof}

>>>>

\begin{lemma}\label{FBLD2TE}
    Let $\R^n$ be equipped with a riemannian metric, and let $c\in\{0,\dots,n\}$. Then for all geodesic disks $D\subset\R^n$ about the origin the intersections
    \begin{enumerate}
        \item $D\cap (\R^{n-c}\times(\R^{c}\smallsetminus\R^{c}_{\geq0}))$
        \item $D \cap (\R^{n-c}\times\R^{c}_{>0})$
    \end{enumerate}
    are disks.
\end{lemma}
\begin{proof}
    Let us suppose $n=c$ for simplicity. For $r>0$, recall the diffeomorphism $[0,r)\to[0,\infty)$, $x\mapsto\frac{x}{r-x}$. In the same way, $\rho_r\colon B_r\to\R^n$, $v\mapsto \frac{d(0,v)}{r-d(0,v)}v$ is a diffeomorphism from the disk $B_r=\{x:\R^n : d(0,x)<r\}$ of radius $r$ about the origin to all of $\R^n$, where $d$ is the metric associated with the given riemannian metric. Now we need only note that $\rho_r$ restricts to diffeomorphisms $B_r\cap\R^n_{>0}\to\R^n_{>0}$ and $B_r\cap(\R^n\smallsetminus\R^n_{\geq0})\to\R^n\smallsetminus\R^n_{\geq0}$, and that both targets are disks.
\end{proof}
